PANCHANGE_data_preprocessing

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
RAMP mhd section finished

edgi.mhd.raw.id <- edgi.mhd.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.atypical_bulimia_nervosa,
    mhd.bingeeating_disorder,
    mhd.atypical_bingeeating_disorder,
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

@@

```{r Check eating_disorders}
if(EDGI == TRUE) {
mhd.raw.id %>%
  select(
    eating_disorders,
    eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    restricting_vs_binge_eating_eating_disorders_numeric,
    mhd.anorexia_nervosa_numeric,
    mhd.atypical_anorexia_nervosa_numeric,
    mhd.bulimia_nervosa_numeric,
    mhd.bingeeating_disorder_numeric,
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.atypical_bulimia_nervosa,
    mhd.bingeeating_disorder,
    mhd.atypical_bingeeating_disorder,
  )
}
```

### Obsessive compulsive disorders
```{r mhd obsessive_compulsive_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    obsessive_compulsive_disorders_numeric =
      case_when(
        mhd.obsessivecompulsive_disorder_ocd_numeric == "1" ~ 1,
        mhd.obsessive_compulsive_related_disorders_numeric == "1" ~ 1,
        mhd.body_dysmorphic_disorder_bdd_numeric == "1" ~ 1,
        (mhd.obsessivecompulsive_disorder_ocd_numeric == "0" &
        mhd.obsessive_compulsive_related_disorders_numeric == "0" &
        mhd.body_dysmorphic_disorder_bdd_numeric == "0") ~ 0
      )
  )

@@

```{r Check obsessive_compulsive_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id %>%
  select(
    obsessive_compulsive_disorders,
    obsessive_compulsive_disorders_numeric,
    mhd.obsessivecompulsive_disorder_ocd,
    mhd.obsessivecompulsive_disorder_ocd_numeric,
    mhd.obsessive_compulsive_related_disorders,
    mhd.obsessive_compulsive_related_disorders_numeric,
    mhd.body_dysmorphic_disorder_bdd,
    mhd.body_dysmorphic_disorder_bdd_numeric
  )
}
```

@@

Create new dataframe with the derived categories
++KT: do we want to keep individual diagnoses here as well?? 
```{r mhd categories}
if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.categories <- mhd.raw.id %>%
  select(
    Sample,
    ID,
    anxiety_disorders_numeric,
    anxiety_disorders,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.social_anxiety_or_social_phobia,
    agoraphobia_panic_disorder_numeric,
    agoraphobia_panic_disorder,
    depressive_disorders_numeric,
    depressive_disorders,
    eating_disorders_numeric,
    eating_disorders,
    obsessive_compulsive_disorders_numeric,
    obsessive_compulsive_disorders,
    psychotic_disorders_numeric,
    psychotic_disorders,
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhd.mania_hypomania_bipolar_or_manicdepression,
    mhd.posttraumatic_stress_disorder_ptsd_numeric,
    mhd.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
    mhd.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.attention_deficit_hyperactivity_disorder_numeric,
    mhd.attention_deficit_hyperactivity_disorder,
    mhd.personality_disorder_numeric,
    mhd.personality_disorder,
    personality_cluster_a_numeric,
    personality_cluster_a,
    personality_cluster_b_numeric,
    personality_cluster_b,
    personality_cluster_c_numeric,
    personality_cluster_c,
    depression_and_anxiety_numeric,
    depression_and_anxiety,
    restricting_vs_binge_eating_eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    bipolar_and_schizophrenia_numeric,
    bipolar_and_schizophrenia,
    control_numeric,
    control,
    disorders_total_count,
    comorbidity_total_count_numeric,
    comorbidity_total_count_factor_numeric,
    comorbidity_total_count_factor
    )
}
```

```{r mhd categories}
if(EDGI == TRUE) {
mhd.raw.categories <- mhd.raw.id %>%
  select(
    Sample,
    ID,
    anxiety_disorders_numeric,
    anxiety_disorders,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.social_anxiety_or_social_phobia,
    agoraphobia_panic_disorder_numeric,
    agoraphobia_panic_disorder,
    depressive_disorders_numeric,
    depressive_disorders,
    eating_disorders_numeric,
    eating_disorders,
    obsessive_compulsive_disorders_numeric,
    obsessive_compulsive_disorders,
    psychotic_disorders_numeric,
    psychotic_disorders,
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhd.mania_hypomania_bipolar_or_manicdepression,
    mhd.posttraumatic_stress_disorder_ptsd_numeric,
    mhd.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
    mhd.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.attention_deficit_hyperactivity_disorder_numeric,
    mhd.attention_deficit_hyperactivity_disorder,
    mhd.personality_disorder_numeric,
    mhd.personality_disorder,
#    personality_cluster_a_numeric,
#    personality_cluster_a,
#    personality_cluster_b_numeric,
#    personality_cluster_b,
#    personality_cluster_c_numeric,
#    personality_cluster_c,
    depression_and_anxiety_numeric,
    depression_and_anxiety,
    restricting_vs_binge_eating_eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    bipolar_and_schizophrenia_numeric,
    bipolar_and_schizophrenia,
    control_numeric,
    control,
    disorders_total_count,
    comorbidity_total_count_numeric,
    comorbidity_total_count_factor_numeric,
    comorbidity_total_count_factor
    ) %>%
  add_column(
    personality_cluster_a_numeric = NA_real_,
    personality_cluster_a = NA_real_,
    personality_cluster_b_numeric = NA_real_,
    personality_cluster_b = NA_real_,
    personality_cluster_c_numeric = NA_real_,
    personality_cluster_c = NA_real_,    
  )
}
```

>>>>

edgi.mhd.raw.id <- edgi.mhd.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.atypical_bulimia_nervosa,
    mhd.bingeeating_disorder,
    mhd.atypical_bingeeating_disorder
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

@@

## RAMP
```{r ramp mhd cols}
if(RAMP == TRUE) {
ramp.mhd.raw <- readRDS(file = paste0(data.raw_path,"/ramp/mhd_ramp.rds"))
dim(ramp.mhd.raw)
colnames(ramp.mhd.raw)
}
```

```{r ramp mhd cleaning}
if(RAMP == TRUE) {
exclude_cols <- c("Sample",
                  "ID")

ramp.mhd.raw.id <- ramp.mhd.raw %>%
  drop_na(`Login ID`) %>% # Drop NAs
  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  separate(ID, into = "ID", sep = 7) %>%
  mutate(
    ID = as.numeric(ID)) %>%
  select(
    Sample, # Sample
    ID, # ID
    mhd.depression = NA.30.depression,
    mhd.pregnancy_depression = NA.30.pregnancy_depression,
    mhd.premenstrual_dysphoric_disorder_pmdd = NA.30.premenstrual_dysphoric_disorder_pmdd,
    mhd.mania_hypomania_bipolar_or_manicdepression = NA.30.mania_hypomania_bipolar_or_manicdepression,
    mhd.anxiety_nerves_or_generalised_anxiety_disorder = NA.30.anxiety_nerves_or_generalised_anxiety_disorder,
    mhd.social_anxiety_or_social_phobia = NA.30.social_anxiety_or_social_phobia,
    mhd.specific_phobia_e.g._phobia_of_flying = NA.30.specific_phobia_e.g._phobia_of_flying,
    mhd.agoraphobia = NA.30.agoraphobia,
    mhd.panic_disorder = NA.30.panic_disorder,
    mhd.panic_attacks = NA.30.panic_attacks,
    mhd.posttraumatic_stress_disorder_ptsd = NA.30.posttraumatic_stress_disorder_ptsd,
    mhd.obsessivecompulsive_disorder_ocd = NA.30.obsessivecompulsive_disorder_ocd, 
    mhd.body_dysmorphic_disorder_bdd = NA.30.body_dysmorphic_disorder_bdd,
    mhd.skin_picking_obsessive_compulsive = NA.30.skin_picking_obsessive_compulsive,
    mhd.anorexia_nervosa = NA.30.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa = NA.30.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa = NA.30.bulimia_nervosa,
    mhd.bingeeating_disorder = NA.30.psychological_overeating_or_bingeeating_disorder,
    mhd.schizophrenia = NA.30.schizophrenia,
    mhd.schizoaffective_disorder = NA.30.schizoaffective_disorder,
    mhd.type_psychosis_psychotic_illness = NA.30.psychosis_type_psychotic_illness,
    mhd.personality_disorder = NA.30.personality_disorder,
    mhd.autism_aspergers_or_autistic_spectrum_disorder = NA.30.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.attention_deficit_hyperactivity_disorder = NA.30.attention_deficit_hyperactivity_disorder,
    mhd.personality_disorder_diagnosed = NA.30.personality_disorder_diagnosed
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(ramp.mhd.raw.id)
# Inspect colnames
colnames(ramp.mhd.raw.id)
#Differences
dim(ramp.mhd.raw)[1]-dim(ramp.mhd.raw.id)[1]
}
```

```{r ramp mhd copy}
if(RAMP == TRUE) {
  mhd.raw.id <- ramp.mhd.raw.id
}
```

@@

```{r Check eating_disorders}
if(EDGI == TRUE) {
mhd.raw.id %>%
  select(
    eating_disorders,
    eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    restricting_vs_binge_eating_eating_disorders_numeric,
    mhd.anorexia_nervosa_numeric,
    mhd.atypical_anorexia_nervosa_numeric,
    mhd.bulimia_nervosa_numeric,
    mhd.bingeeating_disorder_numeric,
    mhd.anorexia_nervosa,
    mhd.atypical_anorexia_nervosa,
    mhd.bulimia_nervosa,
    mhd.atypical_bulimia_nervosa,
    mhd.bingeeating_disorder,
    mhd.atypical_bingeeating_disorder
  )
}
```

### Obsessive compulsive disorders
```{r mhd obsessive_compulsive_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    obsessive_compulsive_disorders_numeric =
      case_when(
        mhd.obsessivecompulsive_disorder_ocd_numeric == "1" ~ 1,
        mhd.obsessive_compulsive_related_disorders_numeric == "1" ~ 1,
        mhd.body_dysmorphic_disorder_bdd_numeric == "1" ~ 1,
        (mhd.obsessivecompulsive_disorder_ocd_numeric == "0" &
        mhd.obsessive_compulsive_related_disorders_numeric == "0" &
        mhd.body_dysmorphic_disorder_bdd_numeric == "0") ~ 0
      )
  )

@@

```{r mhd obsessive_compulsive_disorders for ramp}
if(RAMP == TRUE) {
mhd.raw.id <- mhd.raw.id %>%
  mutate(
    obsessive_compulsive_disorders_numeric =
      case_when(
        mhd.obsessivecompulsive_disorder_ocd_numeric == "1" ~ 1,
        mhd.skin_picking_obsessive_compulsive_numeric == "1" ~ 1,
        mhd.body_dysmorphic_disorder_bdd_numeric == "1" ~ 1,
        (mhd.obsessivecompulsive_disorder_ocd_numeric == "0" &
        mhd.skin_picking_obsessive_compulsive_numeric == "0" &
        mhd.body_dysmorphic_disorder_bdd_numeric == "0") ~ 0
      )
  )

```{r Check obsessive_compulsive_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
mhd.raw.id %>%
  select(
    obsessive_compulsive_disorders,
    obsessive_compulsive_disorders_numeric,
    mhd.obsessivecompulsive_disorder_ocd,
    mhd.obsessivecompulsive_disorder_ocd_numeric,
    mhd.obsessive_compulsive_related_disorders,
    mhd.obsessive_compulsive_related_disorders_numeric,
    mhd.body_dysmorphic_disorder_bdd,
    mhd.body_dysmorphic_disorder_bdd_numeric
  )
}
```

```{r Check obsessive_compulsive_disorders ramp}
if(RAMP == TRUE) {
mhd.raw.id %>%
  select(
    obsessive_compulsive_disorders,
    obsessive_compulsive_disorders_numeric,
    mhd.obsessivecompulsive_disorder_ocd,
    mhd.obsessivecompulsive_disorder_ocd_numeric,
    mhd.skin_picking_obsessive_compulsive,
    mhd.skin_picking_obsessive_compulsive_numeric,
    mhd.body_dysmorphic_disorder_bdd,
    mhd.body_dysmorphic_disorder_bdd_numeric
  )
}
```

@@

Create new dataframe with the derived categories
```{r mhd categories}
if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.categories <- mhd.raw.id %>%
  select(
    Sample,
    ID,
    anxiety_disorders_numeric,
    anxiety_disorders,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.social_anxiety_or_social_phobia,
    agoraphobia_panic_disorder_numeric,
    agoraphobia_panic_disorder,
    depressive_disorders_numeric,
    depressive_disorders,
    eating_disorders_numeric,
    eating_disorders,
    obsessive_compulsive_disorders_numeric,
    obsessive_compulsive_disorders,
    psychotic_disorders_numeric,
    psychotic_disorders,
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhd.mania_hypomania_bipolar_or_manicdepression,
    mhd.posttraumatic_stress_disorder_ptsd_numeric,
    mhd.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
    mhd.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.attention_deficit_hyperactivity_disorder_numeric,
    mhd.attention_deficit_hyperactivity_disorder,
    mhd.personality_disorder_numeric,
    mhd.personality_disorder,
    personality_cluster_a_numeric,
    personality_cluster_a,
    personality_cluster_b_numeric,
    personality_cluster_b,
    personality_cluster_c_numeric,
    personality_cluster_c,
    depression_and_anxiety_numeric,
    depression_and_anxiety,
    restricting_vs_binge_eating_eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    bipolar_and_schizophrenia_numeric,
    bipolar_and_schizophrenia,
    control_numeric,
    control,
    disorders_total_count,
    comorbidity_total_count_numeric,
    comorbidity_total_count_factor_numeric,
    comorbidity_total_count_factor
    )
}
```

```{r mhd categories}
if(EDGI == TRUE) {
mhd.raw.categories <- mhd.raw.id %>%
  select(
    Sample,
    ID,
    anxiety_disorders_numeric,
    anxiety_disorders,
    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
    mhd.specific_phobia_e.g._phobia_of_flying,
    mhd.social_anxiety_or_social_phobia_numeric,
    mhd.social_anxiety_or_social_phobia,
    agoraphobia_panic_disorder_numeric,
    agoraphobia_panic_disorder,
    depressive_disorders_numeric,
    depressive_disorders,
    eating_disorders_numeric,
    eating_disorders,
    obsessive_compulsive_disorders_numeric,
    obsessive_compulsive_disorders,
    psychotic_disorders_numeric,
    psychotic_disorders,
    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhd.mania_hypomania_bipolar_or_manicdepression,
    mhd.posttraumatic_stress_disorder_ptsd_numeric,
    mhd.posttraumatic_stress_disorder_ptsd,
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
    mhd.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.attention_deficit_hyperactivity_disorder_numeric,
    mhd.attention_deficit_hyperactivity_disorder,
    mhd.personality_disorder_numeric,
    mhd.personality_disorder,
#    personality_cluster_a_numeric,
#    personality_cluster_a,
#    personality_cluster_b_numeric,
#    personality_cluster_b,
#    personality_cluster_c_numeric,
#    personality_cluster_c,
    depression_and_anxiety_numeric,
    depression_and_anxiety,
    restricting_vs_binge_eating_eating_disorders_numeric,
    restricting_vs_binge_eating_eating_disorders,
    bipolar_and_schizophrenia_numeric,
    bipolar_and_schizophrenia,
    control_numeric,
    control,
    disorders_total_count,
    comorbidity_total_count_numeric,
    comorbidity_total_count_factor_numeric,
    comorbidity_total_count_factor
    ) %>%
  add_column(
    personality_cluster_a_numeric = NA_real_,
    personality_cluster_a = NA_real_,
    personality_cluster_b_numeric = NA_real_,
    personality_cluster_b = NA_real_,
    personality_cluster_c_numeric = NA_real_,
    personality_cluster_c = NA_real_    
  )
}
```
